---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# smgenerics

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/smgenerics)](https://cran.r-project.org/package=smgenerics)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/kvasilopoulos/smgenerics.svg?branch=master)](https://travis-ci.org/kvasilopoulos/smgenerics)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kvasilopoulos/smgenerics?branch=master&svg=true)](https://ci.appveyor.com/project/kvasilopoulos/smgenerics)
[![Codecov test coverage](https://codecov.io/gh/kvasilopoulos/smgenerics/branch/master/graph/badge.svg)](https://codecov.io/gh/kvasilopoulos/smgenerics?branch=master)
<!-- badges: end -->

The goal of `smgenerics` is to extend the [generics](https://github.com/r-lib/generics) package for less known methods that are part of statistical modelling and reporting packages.
The motivation is exactly the same, i.e. to reduce educe dependencies by providing a set of generic methods that can be imported.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/smgenerics")
```
## Usage

A very characteristic example is the packages that are using Vector Autoregressive modelling
like `vars` and `svars`. These packages require the the use of `irf`(Impulse Response Funcion) and `hd` (Historical Decomposition) generics to function.

```{r}
library(smgenerics)

irf

fevd
```

To use `smgenerics` with your package, import and re-export the generic.

```{r eval=FALSE}
#' @importFrom smgenerics irf
#' @export
smgenerics::irf
```

---
Please note that the 'smgenerics' project is released with a
  [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
  [Copied to clipboard]
