---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# vargenerics

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/vargenerics)](https://cran.r-project.org/package=vargenerics)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/kvasilopoulos/vargenerics.svg?branch=master)](https://travis-ci.org/kvasilopoulos/vargenerics)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/kvasilopoulos/vargenerics?branch=master&svg=true)](https://ci.appveyor.com/project/kvasilopoulos/vargenerics)
<!-- [![Codecov test coverage](https://codecov.io/gh/kvasilopoulos/vargenerics/branch/master/graph/badge.svg)](https://codecov.io/gh/kvasilopoulos/vargenerics?branch=master) -->
<!-- badges: end -->

The goal of vargenerics is to ...

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/vargenerics")
```
## Usage

```{r}
library(vargenerics)

irf

fevd
```

To use `vargenerics` with your package, import and re-export the generic.

```{r eval=FALSE}
#' @importFrom vargenerics irf
#' @export
vargenerics::irf
```

---
Please note that the 'vargenerics' project is released with a
  [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
  [Copied to clipboard]
